Constructing the transition graphs of interacting hysterons

### 2022-05-18 Paper_draft.tex
Corrected instance where l was not explicitly referred to as transition length & changed notation from all-zero/all-one state to saturated states. Note that down boundary of main loop is now not defined.

We now observe that, because we only consider the switching fields $U_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable. Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche. As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips ($l=1$), then evaluating the possible avalanches for each graph in turn. We refer to the graphs with only $l=1$ transitions as base graphs.\\

>>>>

We now observe that, because we only consider the switching fields $U_i^{+,-}(S)$ to depend on the state $S$ and not on the driving field $U$, the same ordering must apply regardless of whether or not a state is initially stable. Thus, there is only ever one up and down transition from each state, even if the transition is only a part of a longer avalanche. As a result, one can construct the possible graphs more efficiently than in the naive method by first constructing all possible graphs consisting out of single hysteron flips (i.e., transitions with transition length $l=1$), then evaluating the possible avalanches for each graph in turn. We refer to the graphs with only $l=1$ transitions as base graphs.\\
